\section{Specification}
The algorithm for computing MRI-Q matrix is shown in Listing.~\ref{algo}
~\cite{stone2008accelerating}. We want to accelerate the whole computation, 
mainly by loop unrolling and pipelining the inner for-loop. The programmer 
view algorithm C code and input dataset come from the Parboil benchmark 
suite~\cite{stratton2012parboil}. In this project, we will design 
accelerators which can accomodate the three datasets provided by Parboil 
benchmark, and make it capable of dealing with input images with arbitray size.


\subsection{Assessment}
We aim to design accelerators which can implement Q-matrix computation for
arbitrary input image size. The first goal is correctness. The Q-matrix 
computed by our accelerator should match the Q-matrix computed by software 
program. We calculate the difference between every output and its golden 
output, and deem it as a match when the difference is less than a certain
 threshold, otherwise it is an error. And we also set an error\_rate. If 
it is within a specified small value, we deem that our accelerator meet 
the correctness goal. The second goal is performance. We will measure the 
acceleration of our accelerator compared to its software execution running
 on FPGA board. We want our accelerators can be integrated with both Ariane
 core and Leon3 core. The generated RTL through Stratus HLS can be integrated
 and prototyped on FPGA. We will design both baremetal application and Linux 
application, the accelerator should pass both tests. At last we want to 
collect speedup data which indicates the acceleration effect. In achieving 
the second goal, we will do some amount of design space exploration, which 
includes designing accelerators with different area and latency trade-offs. 

\begin{lstlisting}[language=C, caption=Algorithm for computing MRI Q matrix, label=algo]
for (m = 0; m < M; m++) {
    phiMag[m] = rPhi[m]*rPhi[m] +
                iPhi[m]*iPhi[m];
}

for (n = 0; n < 8*N; n++) {
    for (m = 0; m < M; m++) {
        exp = 2*PI*(kx[m] * x[n] +
                    ky[m] * y[n] +
                    kz[m] * z[n];
        rQ[n] += phiMag[m] * cos(exp);
        iQ[n] += phiMag[m] * sin(exp);
    }
}
\end{lstlisting}

\subsection{Milestones}\label{sec:arch}
\label{sec:milestones}


\begin{enumerate}

\item Project proposal (by Feb. 5).

\item Reference application (by Feb. 12).

\item ESP tutorials: \emph{``How to design a single-core SoC''}, and 
  \emph{``How to design an accelerator in SystemC (Cadence Stratus HLS)''} (by Feb. 19).

\item Skeleton generation for accelerator and test apps (by Feb. 19)

\item Accelerator and test apps customization (by Mar. 11)

\item SoC evaluation with RTL simulation (by Mar. 18)

\item SoC evaluation with FPGA prototyping (by Mar. 25)

\item Midterm presentation and report (by Mar. 25)

\item DSE and optimization (by May 13)

\item Final presentation and report (by May 13)

\end{enumerate}


\subsection{Critical Aspects}
\begin{enumerate}

\item Implement sine and cosine functions in for-loop.

\item Try different methods of optimization to reduce latency or decrease area.

\end{enumerate}
